Draft - sGBJ

### 2024-08-12 reporting/master_draft/draft_sgbj.qmd
update figures

```{r results='hide'}
library(tidyverse)
library(survival)
library(ggsurvfit)
library(cowplot)

@@

```{r nbsignbreast, fig.height=5, fig.cap="Number of significant pathways by method."}
plot_breast_nb_genesets <- df_breast_cancer_pathway |> 
  group_by(grade, method) |> 
  summarise(nb_sign_bh = sum(significant_bh),
            nb_sign = sum(significant),
            .groups = "drop") |> 
  tidyr::pivot_longer(cols = starts_with("nb_sign")) |> 
  mutate(method = forcats::fct_rev(method),
         method = forcats::fct_recode(method, "Wald Test" = "Wald"),
         name = factor(name,
                       labels = c("Raw", "Benjamini-Hockberg"),
                       levels = c("nb_sign", "nb_sign_bh"))) |> 
  ggplot(mapping = aes(x = method, fill = method, y = value, linetype = name)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", size = .6) +
  facet_grid(grade ~ ., scales = "free_y") +
  scale_fill_viridis_d(guide = "none") +
  scale_linetype_manual(values = c(1,2)) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  labs(x = "Method",
       y = "Nb of significant pathways",
       linetype = "")
```

@@

plot_pval_breast <- df_breast_cancer_pathway |> 
  left_join(df_sGBJ_rank, by = c("pathway", "grade")) |> 
  ggplot(mapping = aes(x = sGBJ_rank, y = p_value)) +
  geom_point(mapping = aes(color = method)) +
  scale_color_viridis_d(direction = -1) +
  labs(color = "") +
  ggnewscale::new_scale_color() +
  geom_hline(mapping = aes(color = "5% threshold",
                           linetype = "5% threshold", yintercept = 0.05),
                         linewidth = 1) +
  # geom_line(data = df_BH_limit,
  #           linewidth = 1,
  #           mapping = aes(color = "BH limit", linetype = "BH limit")) +
  scale_color_manual(values = c("red", "black")) +
  scale_linetype_manual(values = c(2,1)) +
  labs(color = "", linetype = "") +

@@

@@

```{r kmrembrandt, fig.cap="Kaplan meier curves for Astro, Oligo"}
p_type <- survfit2(Surv(time=OVERALL_SURVIVAL_MONTHS, event=EVENT_OS) ~ DISEASE_TYPE,
               data = df_rembrandt |> 
                 mutate(DISEASE_TYPE = factor(DISEASE_TYPE,
                                              levels = c("OLIGODENDROGLIOMA",
                                                         "ASTROCYTOMA"),
                                              labels = c("Oligo",
                                                         "Astro")))) %>% 
  ggsurvfit(linewidth = 1.1) +
  add_confidence_interval() +
  add_risktable(risktable_stats = "n.risk") +
  scale_color_manual(values = c("#8338EC", "#FFB703")) +
  scale_fill_manual(values = c("#8338EC", "#FFB703")) +
  labs(fill = "", color = "")
```

@@

```{r nbsignrembrandt, fig.height=5, fig.cap="Number of significant pathways by method."}
plot_rembrandt_nb_genesets <- df_rembrandt_pathway |> 
  group_by(grade, method) |> 
  summarise(nb_sign_bh = sum(significant_bh),
            nb_sign = sum(significant),
            .groups = "drop") |> 
  tidyr::pivot_longer(cols = starts_with("nb_sign")) |> 
  mutate(method = forcats::fct_rev(method),
         method = forcats::fct_recode(method, "Wald Test" = "Wald"),
         name = factor(name,
                       labels = c("Raw", "Benjamini-Hockberg"),
                       levels = c("nb_sign", "nb_sign_bh")),
         grade  = forcats::fct_recode(grade,
                                      "Oligo" = "Oligodendroglioma",
                                      "Astro" = "Astrocytoma")) |> 
  ggplot(mapping = aes(x = method, fill = method, y = value, linetype = name)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", size = .6) +
  facet_grid(grade ~ ., scales = "free_y") +
  scale_fill_viridis_d(guide = "none") +
  scale_linetype_manual(values = c(1,2)) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  labs(x = "Method",
       y = "Nb of significant pathways",
       linetype = "")
```

@@

plot_pval_rembrandt <- df_rembrandt_pathway |> 
  left_join(df_sGBJ_rank, by = c("pathway", "grade")) |> 
  ggplot(mapping = aes(x = sGBJ_rank, y = p_value)) +
  geom_point(mapping = aes(color = method)) +
  scale_color_viridis_d(direction = -1) +
  labs(color = "") +
  ggnewscale::new_scale_color() +
  geom_hline(mapping = aes(color = "5% threshold",
                           linetype = "5% threshold", yintercept = 0.05),
                         linewidth = 1) +
  # geom_line(data = df_BH_limit,
  #           linewidth = 1,
  #           mapping = aes(color = "BH limit", linetype = "BH limit")) +
  scale_color_manual(values = c("red", "black")) +
  scale_linetype_manual(values = c(2,1)) +
  labs(color = "", linetype = "") +

>>>>

```{r results='hide'}
library(tidyverse)
library(survival)
library(ggsurvfit)
library(cowplot)
library(gt)

@@

```{r nbsignbreast, fig.height=5, fig.cap="Number of significant pathways by method."}
plot_breast_nb_genesets <- df_breast_cancer_pathway |> 
  group_by(grade, method) |> 
  summarise(nb_sign_bh = sum(significant_bh),
            nb_sign = sum(significant),
            .groups = "drop") |> 
  tidyr::pivot_longer(cols = starts_with("nb_sign")) |> 
  mutate(method = forcats::fct_rev(method),
         method = forcats::fct_recode(method, "Wald Test" = "Wald"),
         name = factor(name,
                       labels = c("Raw", "Benjamini-Hockberg"),
                       levels = c("nb_sign", "nb_sign_bh"))) |> 
  ggplot(mapping = aes(x = method, fill = method, y = value, alpha = name)) +
  geom_bar(stat = "identity", position = position_dodge(), size = .6) +
  facet_grid(grade ~ ., scales = "free_y") +
  scale_fill_viridis_d(guide = "none") +
  scale_linetype_manual(values = c(1,2)) +
  scale_alpha_manual(values = c(0.5, 1)) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  labs(x = "Method",
       y = "Nb of significant pathways",
       alpha = "")
```

@@

plot_pval_breast <- df_breast_cancer_pathway |> 
  filter(p_value != 0) |> 
  left_join(df_sGBJ_rank, by = c("pathway", "grade")) |> 
  ggplot(mapping = aes(x = sGBJ_rank, y = p_value)) +
  geom_point(mapping = aes(color = method)) +
  scale_color_viridis_d(direction = -1) +
  labs(color = "") +
  ggnewscale::new_scale_color() +
  geom_hline(mapping = aes(color = "5% threshold",
                           linetype = "5% threshold", yintercept = 0.05),
                         linewidth = 1) +
  # geom_line(data = df_BH_limit,
  #           linewidth = 1,
  #           mapping = aes(color = "BH limit", linetype = "BH limit")) +
  scale_color_manual(values = c("red", "black")) +
  scale_linetype_manual(values = c(2,1)) +
  labs(color = "", linetype = "") +

@@

```{r}
df_breast_cancer_pathway |> 
  group_by(grade, method) |> 
  summarise(prop_sign = mean(significant_bh)) |> 
  gt::gt() |> 
  tab_header(
    title = "Proportion of significant pathway by method and glioma"
  ) %>%
  fmt_number(
    columns = prop_sign,
    decimals = 3
  )
```

@@

```{r kmrembrandt, fig.cap="Kaplan meier curves for Astro, Oligo"}
p_type <- survfit2(Surv(time=OVERALL_SURVIVAL_MONTHS, event=EVENT_OS) ~ DISEASE_TYPE,
               data = df_rembrandt |> 
                 mutate(DISEASE_TYPE = factor(DISEASE_TYPE,
                                              levels = c("OLIGODENDROGLIOMA",
                                                         "ASTROCYTOMA"),
                                              labels = c("Oligo",
                                                         "Astro")))) %>% 
  ggsurvfit(linewidth = 1.1) +
  add_confidence_interval() +
  add_risktable(risktable_stats = "n.risk") +
  scale_color_manual(values = c("#2191FB", "#E94F37")) +
  scale_fill_manual(values = c("#2191FB", "#E94F37")) +
  labs(fill = "", color = "")
```

@@

```{r}
df_rembrandt_pathway |> 
  group_by(grade, method) |> 
  summarise(prop_sign = mean(significant_bh)) |> 
  gt::gt() |> 
  tab_header(
    title = "Proportion of significant pathway by method and glioma"
  ) %>%
  fmt_number(
    columns = prop_sign,
    decimals = 3
  )
```

```{r nbsignrembrandt, fig.height=5, fig.cap="Number of significant pathways by method."}
plot_rembrandt_nb_genesets <- df_rembrandt_pathway |> 
  group_by(grade, method) |> 
  summarise(nb_sign_bh = sum(significant_bh),
            nb_sign = sum(significant),
            .groups = "drop") |> 
  tidyr::pivot_longer(cols = starts_with("nb_sign")) |> 
  mutate(method = forcats::fct_rev(method),
         method = forcats::fct_recode(method, "Wald Test" = "Wald"),
         name = factor(name,
                       labels = c("Raw", "Benjamini-Hockberg"),
                       levels = c("nb_sign", "nb_sign_bh")),
         grade  = forcats::fct_recode(grade,
                                      "Oligo" = "Oligodendroglioma",
                                      "Astro" = "Astrocytoma")) |> 
  ggplot(mapping = aes(x = method, fill = method, y = value, alpha = name)) +
  geom_bar(stat = "identity", position = position_dodge(), size = .6) +
  facet_grid(grade ~ ., scales = "free_y") +
  scale_alpha_manual(values = c(0.5, 1)) +
  scale_fill_viridis_d(guide = "none") +
  scale_linetype_manual(values = c(1,2)) +
  theme_minimal() +
  theme(axis.text.x=element_text(angle = 45, hjust = 1),
        legend.position = "bottom") +
  labs(x = "Method",
       y = "Nb of significant pathways",
       alpha = "")
```

@@

plot_pval_rembrandt <- df_rembrandt_pathway |> 
  filter(p_value != 0) |> 
  left_join(df_sGBJ_rank, by = c("pathway", "grade")) |> 
  ggplot(mapping = aes(x = sGBJ_rank, y = p_value)) +
  geom_point(mapping = aes(color = method)) +
  scale_color_viridis_d(direction = -1) +
  labs(color = "") +
  ggnewscale::new_scale_color() +
  geom_hline(mapping = aes(color = "5% threshold",
                           linetype = "5% threshold", yintercept = 0.05),
                         linewidth = 1) +
  # geom_line(data = df_BH_limit,
  #           linewidth = 1,
  #           mapping = aes(color = "BH limit", linetype = "BH limit")) +
  scale_color_manual(values = c("red", "black")) +
  scale_linetype_manual(values = c(2,1)) +
  labs(color = "", linetype = "") +
